\documentclass[a4paper]{article}

\usepackage[top=1.3cm, bottom=2cm, left=1.3cm, right=1.3cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{xcolor}
\usepackage{lastpage}

\usepackage[hidelinks]{hyperref}

% Profile picture
\usepackage{wrapfig}
\usepackage{graphicx}
% Headers/footers
\usepackage{fancyhdr}

% Font
\usepackage{charter}

\pagestyle{fancy}

\renewcommand{\headrulewidth}{0pt}
\lfoot{\href{https://adriang.se}{https://adriang.se}}
\cfoot{\today}
\rfoot{$^\thepage\! / _{\pageref*{LastPage}}$}

\newcommand{\worktime}[1]{
    \hfill \begin{normalsize}#1\end{normalsize}
}

\newcommand{\school}[2]{\subsection*{#1 \worktime{#2}}}
\newcommand{\employment}[3]{\subsection*{#2 --- \textit{#1} \worktime{#3}}}

\newcommand{\heading}[1]{
    \pdfbookmark{#1}{#1} % necessary for unnumbered sections
    \section*{#1
        \medskip
        \hrule
    }
}

\newcommand{\shorturl}[1]{\href{https://#1}{\texttt{#1}}}

\begin{document}

\noindent
\Huge Adrian Göransson\\
\large \href{https://github.com/adriangoransson}{github.com/adriangoransson}
\hfill +46 709 22 67 19\\
\href{https://www.linkedin.com/in/adriangoransson}{linkedin.com/in/adriangoransson}
\hfill \href{mailto:adrian@adriang.se}{adrian@adriang.se}


\heading{Education}

    \school{Faculty of Engineering, Lund University}{Sep. 2017 -- \emph{est. Jan 2022}}
    Master of Science in Computer Science and Engineering at LTH.
    Highlights so far include courses in concurrent programming, algorithms and data structures, compilers, computer communication, data security and functional programming.

    \school{NTI-Gymnasiet Lund \textnormal{Network technician. Cisco CCNA certified.}}{2010 -- 2013}

\heading{Experience}

    \employment
        {Software developer}
        {Axis Communications}
        {Oct. 2020 -- \emph{Present}}

     Part-time job (Student worker) developing the tools used at Axis for in-device diagnostics.
     Development primarily in Go.

    \employment
        {Teaching assistant}
        {Lund University}
        {Sep. 2020 -- Oct. 2020}

    Teaching assistant for a course in concurrent programming at LTH.
    This course was one of my favorites as a student and helping others get through it and understand the concepts introduced by the course was both challenging and fun.

    \employment
        {Co-founder, developer}
        {Bitiq}
        {Feb. 2018 -- Mar. 2019}

    Ticket sales platform for student hosted events in Lund. We built a serverless REST api in Go and used Postgres as a database. Web apps developed with Vue were used for purchases, event administration and ticket verification using QR scanning.

    \employment
        {Software developer}
        {\href{https://www.qlik.com/us/}{Qlik}}
        {Jun. 2018 -- Jul. 2018}

    Summer position where I helped create a proof of concept of a data visualisation tool to further enhance Qlik's data analytics service.
    Built with Vue and Qlik's chart library Picasso.js.

    \employment
        {DevOps}
        {\href{https://www.beepsend.com/}{Beepsend}
        \begin{small}(acquired by Twilio)\end{small}}
        {Jul. 2013 -- Jul. 2016}

    Beepsend, today Twilio Sweden, is a messaging company specialising in SMS. I was part of a small team building our internal and costumer facing REST APIs with PHP and web apps using CoffeeScript/Javascript (with Chaplin.js). Due to my networking background I was also in charge of managing connectivity over VPN and SS7/Sigtran. I helped set up CI pipelines using Jenkins and Docker.

\heading{Skills}

    \begin{itemize}
        \item Experienced programmer in Javascript, Python, Go, PHP and Java.
        \item Some experience with Rust, Scala and Haskell.
        \item Experienced with Linux server management, security and Docker.
        \item Proficient in git and the shell.
    \end{itemize}

\heading{Open source projects}

    \begin{itemize}
        \item
        \href{https://github.com/adriangoransson/renamer}{\textbf{renamer} --- \textit{Rust}}\hfill \href{https://github.com/adriangoransson/renamer}{\texttt{github.com/adriangoransson/renamer}}

        Command line tool to rename multiple files at once. A port of the classic perl utility rename.pl written in Rust.

        \item
        \href{https://nationilund.se}{\textbf{Nation i Lund} --- \textit{Go}}\hfill \shorturl{nationilund.se}

        Clean, fast and easy listing of student nation events in Lund. Works by scraping the official studentlund website. Would later inspire the launch of Bitiq.

        \item \href{https://pomodoro-tracker.netlify.com}{\textbf{Pomodoro tracker} --- \textit{Javascript/Vue}} \hfill \shorturl{pomodoro-tracker.netlify.com}

        Simple but customisable Pomodoro (study technique) ``egg clock''. Works just as well on mobile and desktop. Available offline with service workers and has notification support.
    \end{itemize}

\bigskip
\center \large References available upon request

\end{document}
